Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-06-04 main.tex
Try with labels in subcaptions.

\subsection{Perturbations}
%
We apply external longitudinal forces to the ends of each handlebar using an
adapted Bump'Em system~\cite{Tan2020} which is designed with four motors
working in tandem, Figure~\ref{fig:setup-diagram}. The four motors are
programmed to apply a light force at all times to keep the ropes taught and to
track a commanded force profile using a PID controller running on a
microprocessor (Arduino XXX, Italy). We measure the force applied by each motor
at the handlebar via four inline load cells, each with a max load of
XX~\si{\newton}. The commanded force profiles are designed to apply an external
pulsive torque to the front assembly (handlebars, forks, wheel) at magnitudes
varying from X to X. The four motors are arranged at the four corners of a
1~\si{\meter} wide treadmill (make, Company, City) that can reach speeds of
18~\si{\kilo\meter\per\hour}. The general design is described in detail in the
Van De Velde's MSc thesis~\citep{vandeVelde2022a} and the physical arrangment
is shown in Figure~\ref{fig:participant-in-set-up}. Our modifications relative
to that described in the thesis include simplifying the controller with a
inexpensive microcontroller and the use of a simpler safety harness.
Figure~\ref{fig:perturbation_0} shows an example perturbation.
%
\begin{figure}
  \centering
  % TODO : scale these pngs to a reasonable size for an A4 sheet
  \subcaptionbox{
    A participant on the bicycle in the safety harness with the Bump'Em motor
    lines attached to the ends of the handlebars.
    % TODO : This label causes a compile error. I think this is where it is
    % supposed to go.
    %\label{fig:participant-in-set-up}
  }{
    \includegraphics[width=75mm]{figures/participant-in-set-up.png}
  }
  \subcaptionbox{
    Top view diagram of bicycle handlebar perturbation system.
    %\label{fig:setup-diagram}
  }{
    \includegraphics[width=65mm]{figures/setup-diagram.png}
  }
  \label{fig:experimental-setup}
\end{figure}

@@

The coefficient estimates for a single-level logistic regression at
6~\unit{\kilo\meter\per\hour} with gain $k=10$ are shown in
Table~\ref{table:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors. Larger
angular impulse increases the probability to fall and enduring more
perturbations or having the balance assist on, decrease the probability to
fall.  The associated multiplicative change in odds are shown in
Table~\ref{table:freq-change-in-odds-6}.

@@

The coefficient estimates for a single-level logistic regression at
10~\si{\kilo\meter\per\hour} with gain $k=8$ are shown in Table
\ref{table:freq-coefs}. The angular impulse and perturbation order are
statistically significant predictors. Larger angular impulse increases the
probability to fall and enduring more perturbations decreases the probability
to fall. The associated multiplicative change in odds are shown in
Table~\ref{table:freq-change-in-odds}.

>>>>

\subsection{Perturbations}
%
We apply external longitudinal forces to the ends of each handlebar using an
adapted Bump'Em system~\cite{Tan2020} which is designed with four motors
working in tandem, Figure~\ref{fig:setup-diagram}. The four motors are
programmed to apply a light force at all times to keep the ropes taught and to
track a commanded force profile using a PID controller running on a
microprocessor (Arduino XXX, Italy). We measure the force applied by each motor
at the handlebar via four inline load cells, each with a max load of
XX~\si{\newton}. The commanded force profiles are designed to apply an external
pulsive torque to the front assembly (handlebars, forks, wheel) at magnitudes
varying from X to X. The four motors are arranged at the four corners of a
1~\si{\meter} wide treadmill (make, Company, City) that can reach speeds of
18~\si{\kilo\meter\per\hour}. The general design is described in detail in the
Van De Velde's MSc thesis~\citep{vandeVelde2022a} and the physical arrangment
is shown in Figure~\ref{fig:participant-in-set-up}. Our modifications relative
to that described in the thesis include simplifying the controller with a
inexpensive microcontroller and the use of a simpler safety harness.
Figure~\ref{fig:perturbation_0} shows an example perturbation.
%
\begin{figure}
  \centering
  % TODO : scale these pngs to a reasonable size for an A4 sheet
  \subcaptionbox{A participant on the bicycle in the safety harness with the
    Bump'Em motor lines attached to the ends of the
    handlebars.\label{fig:participant-in-set-up}}
    {\includegraphics[width=75mm]{figures/participant-in-set-up.png}}
  \subcaptionbox{Top view diagram of bicycle handlebar perturbation
    system.\label{fig:setup-diagram}}
    {\includegraphics[width=65mm]{figures/setup-diagram.png}}
  \label{fig:experimental-setup}
\end{figure}

@@

The coefficient estimates for a single-level logistic regression at
6~\unit{\kilo\meter\per\hour} with gain $k=10$ are shown in
Table~\ref{table:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors. Larger
angular impulse increases the probability to fall and enduring more
perturbations or having the balance assist on, decrease the probability to
fall.  The associated multiplicative change in odds are shown in
Table~\ref{table:freq-coefs-6}.

@@

The coefficient estimates for a single-level logistic regression at
10~\si{\kilo\meter\per\hour} with gain $k=8$ are shown in Table
\ref{table:freq-coefs}. The angular impulse and perturbation order are
statistically significant predictors. Larger angular impulse increases the
probability to fall and enduring more perturbations decreases the probability
to fall. The associated multiplicative change in odds are shown in
Table~\ref{table:freq-coefs}.
